graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-05-09 paper/paper.tex
correct figure formatting and labels  (fig2-4, pane B-D)

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state =}\StringTok{"activating"}\NormalTok{, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node =} \DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Activating pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.05}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node =} \DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) Inhibiting pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# activating graph}
\NormalTok{state <-}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\KeywordTok{length}\NormalTok{(}\KeywordTok{E}\NormalTok{(graph)))}
\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node=}\DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow=}\DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Activating pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\NormalTok{op <-}\StringTok{ }\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow=}\KeywordTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{), }\DataTypeTok{mar=}\KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{,}\DecValTok{1}\NormalTok{), }\DataTypeTok{oma=}\KeywordTok{c}\NormalTok{(}\FloatTok{0.5}\NormalTok{,}\FloatTok{0.5}\NormalTok{,}\FloatTok{0.5}\NormalTok{,}\DecValTok{0}\NormalTok{))}
\CommentTok{#plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\CommentTok{#plot sigma matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_sigma_mat_dist_graph}\NormalTok{(graph, }\FloatTok{0.8}\NormalTok{, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(c) "}\NormalTok{, Sigma, }\StringTok{" matrix"}\NormalTok{)), }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\CommentTok{#plot simulated correlations}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{cor}\NormalTok{(}\KeywordTok{t}\NormalTok{(expr)), }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(d) Simulated correlation"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\NormalTok{op <-}\StringTok{ }\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow=}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }\DataTypeTok{mar=}\KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{,}\DecValTok{1}\NormalTok{), }\DataTypeTok{oma=}\KeywordTok{c}\NormalTok{(}\FloatTok{0.5}\NormalTok{,}\FloatTok{0.5}\NormalTok{,}\FloatTok{0.5}\NormalTok{,}\DecValTok{0}\NormalTok{))}
\CommentTok{#plot simulated expression data}
\KeywordTok{heatmap.2}\NormalTok{(expr, }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{bluered}\NormalTok{(}\DecValTok{50}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(e) Simulated expression data (log scale)"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{par}\NormalTok{(op)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{#generate parameters for inhibitions}
\NormalTok{state <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{-1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{-1}\NormalTok{)}
\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node=}\DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow=}\DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Inhibiting pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\CommentTok{# #plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\CommentTok{# #plot sigma matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_sigma_mat_dist_graph}\NormalTok{(graph, }\DataTypeTok{state =}\NormalTok{ state, }\FloatTok{0.8}\NormalTok{, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"blue"}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(c) "}\NormalTok{, Sigma, }\StringTok{" matrix"}\NormalTok{)), }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\CommentTok{#plot simulated correlations}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{cor}\NormalTok{(}\KeywordTok{t}\NormalTok{(expr)), }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"blue"}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(d) Simulated correlation"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\DecValTok{3}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

>>>>

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state =}\StringTok{"activating"}\NormalTok{, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node =} \DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Activating pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.05}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node =} \DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) Inhibiting pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# activating graph}
\NormalTok{state <-}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\KeywordTok{length}\NormalTok{(}\KeywordTok{E}\NormalTok{(graph)))}
\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node=}\DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow=}\DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Activating pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\CommentTok{#plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\CommentTok{#plot sigma matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_sigma_mat_dist_graph}\NormalTok{(graph, }\FloatTok{0.8}\NormalTok{, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(c) "}\NormalTok{, Sigma, }\StringTok{" matrix"}\NormalTok{)), }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\CommentTok{#plot simulated correlations}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{cor}\NormalTok{(}\KeywordTok{t}\NormalTok{(expr)), }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(d) Simulated correlation"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\CommentTok{#plot simulated expression data}
\KeywordTok{heatmap.2}\NormalTok{(expr, }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{bluered}\NormalTok{(}\DecValTok{50}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{labCol =} \StringTok{""}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"samples"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{1.5}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.2}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.5}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"genes"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{4}\NormalTok{, }\DataTypeTok{line=}\DecValTok{1}\NormalTok{, }\DataTypeTok{at=}\OperatorTok{-}\FloatTok{0.4}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.5}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(e) Simulated expression data (log scale)"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{#generate parameters for inhibitions}
\NormalTok{state <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{-1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{-1}\NormalTok{)}
\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state=}\NormalTok{state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{cex.node=}\DecValTok{2}\NormalTok{, }\DataTypeTok{cex.arrow=}\DecValTok{4}\NormalTok{, }\DataTypeTok{arrow_clip =} \FloatTok{0.2}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(a) Inhibiting pathway structure"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\FloatTok{0.075}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\CommentTok{#plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

\CommentTok{# #plot sigma matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_sigma_mat_dist_graph}\NormalTok{(graph, }\DataTypeTok{state =}\NormalTok{ state, }\FloatTok{0.8}\NormalTok{, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"blue"}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(c) "}\NormalTok{, Sigma, }\StringTok{" matrix"}\NormalTok{)), }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\CommentTok{#plot simulated correlations}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{cor}\NormalTok{(}\KeywordTok{t}\NormalTok{(expr)), }\DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"blue"}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(d) Simulated correlation"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
